---
title: "Descriptive_Statistics"
author: "Debit Paudel"
date: "12/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
data_iris <- iris
data_iris
```
The dataset contains 150 observations and 5 variables, representing the length and width of the sepal and petal and the species of 150 flowers.

**Minimum and maximum**. 

  We can find using max() and min () functions.
```{r}
min(data_iris$Sepal.Width)
max(data_iris$Sepal.Width)
```
The **Range** also  gives minimun and maximum.
```{r}
rnge<-range(data_iris$Sepal.Width)
rnge
```

It is shown in like a array.we can differentiate using 
```{r}
rnge[1]
```

**Mean** and **Meadian** can be calculated uding mean() function
```{r}
mean(data_iris$Sepal.Width)
median(data_iris$Sepal.Width)
```
The **First Quartile**,**Third Quartile** as well *IQR* have functions and can be calculated like below:

```{r}
quantile(data_iris$Sepal.Width, 0.25)

```
For the Third quartile we just need to change second parameter as **0.75**

```{r}
IQR(data_iris$Sepal.Width)
```
 **Standard deviation and variance**

 
The standard deviation and the variance is calculated with the sd() and var() functions:

```{r}
sd(data_iris$Sepal.Width)
var(data_iris$Sepal.Width)
```
**Summary**
Summary will give summary for all the variables by just a function summary()

```{r}
summary(data_iris)
```

If we need the descriptive statistics by group we can apply by() function
```{r}
by(data_iris, data_iris$Species, summary)
```


Plotting the histogram for the Sepal width 

```{r}
hist(data_iris$Sepal.Width)
```

**BoxPlot**. 
  
  Box Plots are best because they remove the outliers and ease the descriptive analysis.
  
```{r}
boxplot(data_iris$Sepal.Width ~ data_iris$Species)
```
  **Frequency tables with** freq()
The freq() function produces frequency tables with frequencies, proportions, as well as missing data information.

```{r}
library(summarytools)
freq(data_iris$Species)
```



